\LARGE \bf Longitudinal Trajectory Planning and Tracking for Fixed-Path Autonomous Driving

### 2016-01-13 paper1.tex
got the bib to work

\usepackage[pdftex]{graphicx}
\usepackage[hypcap]{caption}
\usepackage[noadjust]{cite}

@@

For the purposes of this work, two constraints are used for $v_m$: legal speed limit (set constant for the whole path) and lateral acceleration limit. Lateral acceleration constraints are translated into longitudinal speed constraints using the approximation $v_{m,k}(a_{B,y}) = \sqrt{a_{B,y}^{max}/\kappa_k}$ for $k = 1, ..., N_p$. For each path point, the value $v_{m,k}(a_{B,y})$ denotes the speed necessary to obtain the limit lateral acceleration, denoted by $a^{max}_{B,y}$. The value $\kappa_k$ denotes the path curvature at each point. For the sake of simplicity, the values of $a^+_{m,k}$, $a^-_{m,k}$, $j^+_{m,k}$, and $j^-_{m,k}$ are all set constant for the entire path, using recommendations from \cite{Maurya2012}
An arbitrary set of constraints may

@@

@@

\bibliography{HRI_internship_trajectory_planner_articles}
\bibliographystyle{IEEEtran}

>>>>

\usepackage[pdftex]{graphicx}
% \usepackage[hypcap]{caption}
\usepackage[noadjust]{cite}

@@

For the purposes of this work, two constraints are used for $v_m$: legal speed limit (set constant for the whole path) and lateral acceleration limit. Lateral acceleration constraints are translated into longitudinal speed constraints using the approximation $v_{m,k}(a_{B,y}) = \sqrt{a_{B,y}^{max}/\kappa_k}$ for $k = 1, ..., N_p$. For each path point, the value $v_{m,k}(a_{B,y})$ denotes the speed necessary to obtain the limit lateral acceleration, denoted by $a^{max}_{B,y}$. The value $\kappa_k$ denotes the path curvature at each point. For the sake of simplicity, the values of $a^+_{m,k}$, $a^-_{m,k}$, $j^+_{m,k}$, and $j^-_{m,k}$ are all set constant for the entire path, using recommendations from ~\cite{Maurya2012}
An arbitrary set of constraints may

@@

\section*{Acknowledgments}

Thanks.

@@

\bibliographystyle{IEEEtran}
\bibliography{HRI_internship_trajectory_planner_articles}
